---
title: "Inteli nagrody"
subtitle: "wersja skrócona"
date: "11 lutego 2020"
output:
  html_document:
    theme: united
    highlight: kate
    toc: true
    toc_depth: 2
    df_print: paged
    fig_width: 9
    fig_height: 12
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
library(dplyr)
library(patchwork)
```

# Results {.tabset .tabset-fade}

## AIC {.tabset .tabset-fade}

### raw

```{r echo = F, eval = T, fig.height=12, fig.width=7}
fig$aic
```

```{r echo = F, eval = T, fig.height=12, fig.width=7}
fig$aic_
```

### delta

```{r echo = F, eval = T, fig.height=16, fig.width=6}
fig$deltaaic
```

### average

```{r echo = F, eval = T, fig.height=12, fig.width=6}
fig$averageaic
```

## predictions

```{r echo = F, eval=T, fig.height=12, fig.width=6}
fig$prediction + theme_publication + theme(legend.position = "none")
```

## predictions+ {.tabset .tabset-fade}

### basic

```{r echo = F, eval = T, fig.height=12, fig.width=6}
fig$coursebasic
```

### decay+

```{r echo = F, eval = T, fig.height=12, fig.width=7}
fig$`coursedecay+`
```

### fictitious

```{r echo = F, eval = T, fig.height=12, fig.width=7}
fig$coursefictitious
```

### basic4arm

```{r echo = F, eval = T, fig.height=12, fig.width=7}
fig$coursebasic4arm
```

## parameter {.tabset .tabset-fade}

### basic

basic4arm | basic | hbayedDM "bandit2arm"

```{r echo = F, eval = T, fig.height=4, fig.width=8}
(plotparamA("basic4arm")+
  plotparamA("basic")+
  plotparamhbayes("bandit2arm", "A")) *
  theme_publication *
  scale_y_continuous(limits = c(0,1)) *
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

(plotparamB("basic4arm")+
  plotparamB("basic")+
  plotparamhbayes("bandit2arm", "tau")) *
  theme_publication *
  scale_y_continuous(limits = c(0,50)) *
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

```

### dual

dual | hbayesDM "prl_rp"

```{r echo = F, eval = T, fig.height=4, fig.width=8}
(plotparamA("dual") + 
  plotparamhbayes("prl_rp", c("Apun", "Arew"))  + 
  scale_y_continuous(limits = c(0,1)))  * theme(legend.position = "none")*
  theme_publication *
  scale_y_continuous(limits = c(0,1)) *
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

```{r echo = F, eval = T, fig.height=4, fig.width=4}
(plotparamB("dual") + 
  plotparamhbayes("prl_rp", c("beta"))) *
  theme_publication *
  scale_y_continuous(limits = c(0,50)) *
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

### fictitious

fictitious | hbayesDM "prl_fictitious"

```{r echo = F, eval = T, fig.height=4, fig.width=4}
(plotparamA("fictitious") + scale_y_continuous(limits = c(0,1)) +
  paramhbayes[["prl_fictitious"]] %>% 
  mutate(tag = subjID,
         subjID = NULL) %>%
  tidyr::gather(par, value, -tag, -substance) %>%
  filter(par %in% c("alpha")) %>%
  ggplot(aes(x = substance, y = as.numeric(value), fill = substance)) +
  geom_boxplot()+
  facet_wrap(~par, scales = "free_y") +
  scale_y_continuous(limits = c(0,1))) *
  theme_publication *
  scale_y_continuous(limits = c(0,1)) *
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

(plotparamB("fictitious") + scale_y_continuous(limits = c(0,50)) +
  paramhbayes[["prl_fictitious"]] %>% 
  mutate(tag = subjID,
         subjID = NULL) %>%
  tidyr::gather(par, value, -tag, -substance) %>%
  filter(par %in% c("beta")) %>%
  ggplot(aes(x = substance, y = as.numeric(value), fill = substance)) +
  geom_boxplot()+
  facet_wrap(~par, scales = "free_y") +
  scale_y_continuous(limits = c(0,50))) *
  theme_publication *
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

### hybrid

hybrid | hbayesDM "prl_fictitious_rp"

```{r echo = F, eval = T, fig.height=4, fig.width=9}
(plotparamA("hybrid") + 
  plotparamhbayes("prl_fictitious_rp", c("eta_pos","eta_neg","alpha")) + 
  scale_y_continuous(limits = c(0,1))) * theme(legend.position = "none") *
  theme_publication *
  scale_y_continuous(limits = c(0,1)) *
  theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

## hbayes parameters {.tabset .tabset-fade}

### bandit2arm

```{r echo = F, eval = T, fig.height= 5, fig.width=9}
plotInd(resulthbayes$bandit2arm$alcohol, "A") + plotInd(resulthbayes$bandit2arm$alcohol, "tau")  
```


#### alcohol

```{r echo = F, eval = T, fig.height=4, fig.width=7}
plot(resulthbayes$bandit2arm$alcohol) 
```

#### alcoholsaccharin

```{r echo = F, eval = T, fig.height=4, fig.width=7}
plot(resulthbayes$bandit2arm$alcoholsaccharin) 
```

#### saccharin

```{r echo = F, eval = T, fig.height=4, fig.width=7}
plot(resulthbayes$bandit2arm$saccharin) 
```

#### water

```{r echo = F, eval = T, fig.height=4, fig.width=7}
plot(resulthbayes$bandit2arm$saccharin) 
```

### prl_rp (dual)

#### alcohol

```{r echo = F, eval = T, fig.height= 5, fig.width=12}
plotInd(resulthbayes$prl_rp$alcohol, "Apun") + plotInd(resulthbayes$prl_rp$alcohol, "Arew") + plotInd(resulthbayes$prl_rp$alcohol, "beta")  
```

```{r echo = F, eval = T, fig.height=3, fig.width=7}
plot(resulthbayes$prl_rp$alcohol) 
```

#### alcoholsaccharin

```{r echo = F, eval = T, fig.height=3, fig.width=7}
plot(resulthbayes$prl_rp$alcoholsaccharin) 
```

#### saccharin

```{r echo = F, eval = T, fig.height=3, fig.width=7}
plot(resulthbayes$prl_rp$saccharin) 
```

#### water

```{r echo = F, eval = T, fig.height=3, fig.width=7}
plot(resulthbayes$prl_rp$saccharin) 
```

### prl_fictitious (fictitious)

#### alcohol

```{r echo = F, eval = T, fig.height=3, fig.width=7}
plot(resulthbayes$prl_fictitious$alcohol) 
```

#### alcoholsaccharin

```{r echo = F, eval = T, fig.height=3, fig.width=7}
plot(resulthbayes$prl_fictitious$alcoholsaccharin) 
```

#### saccharin

```{r echo = F, eval = T, fig.height=3, fig.width=7}
plot(resulthbayes$prl_fictitious$saccharin) 
```

#### water

```{r echo = F, eval = T, fig.height=3, fig.width=7}
plot(resulthbayes$prl_fictitious$saccharin) 
```

### prl_fictitious_rp (fictitious)

#### alcohol

```{r echo = F, eval = T, fig.height=3, fig.width=9}
plot(resulthbayes$prl_fictitious_rp$alcohol) 
```

#### alcoholsaccharin

```{r echo = F, eval = T, fig.height=3, fig.width=9}
plot(resulthbayes$prl_fictitious_rp$alcoholsaccharin) 
```

#### saccharin

```{r echo = F, eval = T, fig.height=3, fig.width=9}
plot(resulthbayes$prl_fictitious_rp$saccharin) 
```

#### water

```{r echo = F, eval = T, fig.height=3, fig.width=9}
plot(resulthbayes$prl_fictitious_rp$saccharin) 
```

## hbayes fit

```{r eval = FALSE, echo = TRUE}
#Error: Can't mix NA and not NA values in 'r_eff'.
hBayesDM::printFit(
  resulthbayes$bandit2arm$saccharin,
  resulthbayes$prl_fictitious$saccharin, 
  resulthbayes$prl_rp$saccharin,
  resulthbayes$prl_fictitious_rp$saccharin, 
  ic = "looic")
```


***

# Model {.tabset .tabset-fade}

 <!-- .tabset-pills -->

## basic

2arm bandit 

```{r}
  function(par, a) {
  a = a[with(a, order(start)), ]
  nll = 0
  if (par[1] < 0 | par[1] > 1 |
      par[2] < 0 | par[2] > 50) {
    nll = Inf
  } else {
    Q = c(0, 0)
    P <- vector()
    rewards = a$dooropened
    sides = ceiling(a$corner / 2)
    for (i in seq_along(sides)) {
      r = rewards[i]
      s = sides[i]
      if (is.finite(s) & is.finite(r)) {
        P = exp(par[2] * Q) / sum(exp(par[2] * Q))
        if(any(P < .001)){
          index = which(P < .001)
          P[index] = .001; P[-(index)] = .999}
        nll = -log(P[s]) + nll
        pe = r - Q[s]
        Q[s] = Q[s] + (par[1] * pe)}}}
  nll}
```

## dual

learning rate split by reward

```{r}
function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50 |
        par[3] < 0 | par[3] > 1) {
      nll = Inf
    } else {
      Q = c(0, 0)
      P <- vector()
      rewards = a$dooropened
      sides = ceiling(a$corner / 2)
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        if (is.finite(s) & is.finite(r)) {
          P = exp(par[2] * Q) / sum(exp(par[2] * Q))
          if(any(P < .001)){
            index = which(P < .001)
            P[index] = .001; P[-(index)] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          if (r == 1) {Q[s] = Q[s] + (par[1] * pe)
          } else {Q[s] = Q[s] + (par[3] * pe)}}}}
    nll}
```

## attention

lerning rate related to prediction error

```{r}
function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50 |
        par[3] < 0 | par[3] > 1) {
      nll = Inf
    } else {
      Q = c(0, 0)
      P <- vector()
      rewards = a$dooropened
      sides = ceiling(a$corner / 2)
      alpha.zero = par[1]
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        if (is.finite(s) & is.finite(r)) {
          P = exp(par[2] * Q) / sum(exp(par[2] * Q))
          if(any(P < .001)){
            index = which(P < .001)
            P[index] = .001; P[-(index)] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          alpha = par[3] * abs(pe) + (1 - par[3]) * alpha.zero
          Q[s] = Q[s] + (alpha * pe)}}}
    nll}
```

## fictitious

subsequent update of nonchosen alternative

```{r}
function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if ((par[1] < 0 | par[1] > 1) |
        (par[2] < 0 | par[2] > 50)) {
      nll = Inf
    } else {
      Q = c(0, 0)
      P <- vector()
      rewards = a$dooropened
      sides = ceiling(a$corner / 2)
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        if (is.finite(s) & is.finite(r)) {
          P = exp(par[2] * Q) / sum(exp(par[2] * Q))
          if(any(P < .001)){
            index = which(P < .001)
            P[index] = .001; P[-(index)] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          Q[s] = Q[s] + (par[1] * pe)
          Q[-s] = Q[-s] - (par[1] * pe)}}}
    nll}
```

## hybrid

fictitious update and split learning rate

```{r}
function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50 |
        par[3] < 0 | par[3] > 1) {
      nll = Inf
    } else {
      Q = c(0, 0)
      P <- vector()
      rewards = a$dooropened
      sides = ceiling(a$corner / 2)
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        if (is.finite(s) & is.finite(r)) {
          P = exp(par[2] * Q) / sum(exp(par[2] * Q))
          if(any(P < .001)){
            index = which(P < .001)
            P[index] = .001; P[-(index)] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          if (r == 1) {
            Q[s] = Q[s] + (par[1] * pe)
            Q[-s] = Q[-s] - (par[1] * pe)
          } else {
            Q[s] = Q[s] + (par[3] * pe)
            Q[-s] = Q[-s] - (par[3] * pe)}}}}
    nll}
```

## forgetful

applied Collins et al. idea of forgetting `{cit}`

```{r}
function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50 |
        par[3] < 0 | par[3] > 1) {
      nll = Inf
    } else {
      Q = c(0, 0)
      P <- vector()
      rewards = a$dooropened
      sides = ceiling(a$corner / 2)
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        if (is.finite(s) & is.finite(r)) {
          P = exp(par[2] * Q) / sum(exp(par[2] * Q))
          if(any(P < .001)){
            index = which(P < .001)
            P[index] = .001; P[-(index)] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          Q[s] = Q[s] + par[1] * pe
          delta = 0.5 - Q[s]
          Q[s] = Q[s] + par[3] * delta
          Q[-s] = Q[-s] + par[3] * delta}}}
    nll}
```

## decay

decay of expected reward along with time, for both sides

```{r}
function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50 |
        par[3] < 0 | par[3] > 1) {
      nll = Inf
    } else {
      # temp = nrow(a)
      tempQ = c()
      Q = c(0, 0)
      date = rep(a$start[1], 2)
      t = c(0, 0)
      P <- vector()
      rewards = a$dooropened
      sides = ceiling(a$corner/2)
      nows = a$start
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        now = nows[i]
        t = as.numeric(difftime(now, date, units = 'mins'))
        date[s] = now
        if (is.finite(s) & is.finite(r)) {
          Q[s] = exp( -(t[s]) * par[3] ) * Q[s]
          tempQ = exp( -(t[-s]) * par[3] ) * Q[-s]
          P[s] = exp(par[2] * Q[s]) / 
            (sum(exp(par[2] * Q[s]), exp(par[2] * tempQ)))
          if(P[s] < .001){P[s] = .001}
          if(P[s] > .999){P[s] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          Q[s] = Q[s] + (par[1] * pe)}}}
    nll}
```

## decay+

```{r}
function(par, a) {
  a = a[with(a, order(start)), ]
  nll = 0
  if (par[1] < 0 | par[1] > 1 |
      par[2] < 0 | par[2] > 50 |
      par[3] < 0 | par[3] > 1 |
      par[4] < 0 | par[4] > 1) {
    nll = Inf
  } else {
    tempQ = c()
    Q = c(0, 0)
    date = rep(a$start[1], 2)
    t = c(0, 0)
    P <- vector()
    rewards = a$dooropened
    sides = ceiling(a$corner/2)
    nows = a$start
    rew = c(0,0)
    for (i in seq_along(sides)) {
      r = rewards[i]
      s = sides[i]
      now = nows[i]
      t = as.numeric(difftime(now, date, units = 'mins'))
      date[s] = now
      if (is.finite(s) & is.finite(r)) {
        decay = ifelse(rew == 1, par[3], par[4])
        Q[s] = exp( -(t[s]) * decay[s] ) * Q[s]
        tempQ = exp( -(t[-s]) * decay[-s] ) * Q[-s]
        P[s] = exp(par[2] * Q[s]) / 
          (sum(exp(par[2] * Q[s]), exp(par[2] * tempQ)))
        if(P[s] < .001){P[s] = .001}
        if(P[s] > .999){P[s] = .999}
        nll = -log(P[s]) + nll
        pe = r - Q[s]
        Q[s] = Q[s] + (par[1] * pe)
        Q[-s] = Q[-s] + (par[1] * pe)
        rew[s] = r}}}
  nll}
```

## decay++

also decay with threshold (combined functions)

```{r}
function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50 |
        par[3] < 0 | par[3] > 1 |
        par[4] < 0 | par[4] > 1 |
        par[5] < 1 | par[5] > 60) {
      nll = Inf
    } else {
      tempQ = c()
      Q = c(0, 0)
      date = rep(a$start[1], 2)
      t = c(0, 0)
      P <- vector()
      rewards = a$dooropened
      sides = ceiling(a$corner/2)
      nows = a$start
      rew = c(0,0)
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        now = nows[i]
        t = as.numeric(difftime(now, date, units = 'mins'))
        date[s] = now
        if (is.finite(s) & is.finite(r)) {
          decay = ifelse(rew == 1, par[3], par[4])
          if(t[s] > par[5]){ 
            Q[s] = exp( -(t[s]) * decay[s] ) * Q[s]}
          tempQ = ifelse(t[-s] > par[5], 
            exp( -(t[-s]) * decay[-s] ) * Q[-s],
            Q[-s])
          P[s] = exp(par[2] * Q[s]) / 
            (sum(exp(par[2] * Q[s]), exp(par[2] * tempQ)))
          if(P[s] < .001){P[s] = .001}
          if(P[s] > .999){P[s] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          Q[s] = Q[s] + (par[1] * pe)
          rew[s] = r}}}
    nll}
```

## old decay

which was wrong

```{r}
  function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50 |
        par[3] < 0 | par[3] > 1) {
      nll = Inf
    } else {
      temp = nrow(a)
      tempQ = c()
      Q = c(0, 0)
      date = rep(a$start[1], 2)
      t = c(0, 0)
      P <- vector()
      for (i in seq_along(1:temp)) {
        r = a$dooropened[i]
        s = ceiling(a$corner[i] / 2)
        now = a$start[i]
        t[1] = as.numeric(difftime(now, date[1], units = 'mins'))
        t[2] = as.numeric(difftime(now, date[2], units = 'mins'))
        date[s] = now
        if (is.finite(s) & is.finite(r)) {
          P[s] = exp(par[2] * Q[s]) /  
            (sum(exp(par[2] * Q[s]), exp(par[2] * tempQ)))
          if(P[s] < .001){P[s] = .001}
          if(P[s] > .999){P[s] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          Q[s] = Q[s] + (par[1] * pe)
          Q[s] = exp( -(t[s]) * par[3] ) * Q[s]
          tempQ = exp( -(t[-s]) * par[3] ) * Q[-s]}}}
    nll}
```

## decay blank

learning rate set as 1

```{r}
function(par, a) {
  a = a[with(a, order(start)), ]
  nll = 0
  if (par[1] < 0 | par[1] > 50 |
      par[2] < 0 | par[2] > 1) {
    nll = Inf
  } else {
    Q = c(0, 0)
    date = rep(a$start[1], 2)
    t = c(0, 0)
    P <- vector()
    rewards = a$dooropened
    sides = ceiling(a$corner/2)
    nows = a$start
    for (i in seq_along(sides)) {
      r = rewards[i]
      s = sides[i]
      now = nows[i]
      t = as.numeric(difftime(now, date, units = 'mins'))
      date[s] = now
      if (is.finite(s) & is.finite(r)) {
        Q[s] = exp( -(t[s]) * par[2] ) * Q[s]  
        tempQ = exp( -(t[-s]) * par[2] ) * Q[-s]
        P[s] = exp(par[1] * Q[s]) / 
          (sum(exp(par[1] * Q[s]), exp(par[1] * tempQ)))
        if(P[s] < .001){P[s] = .001}
        if(P[s] > .999){P[s] = .999}
        nll = -log(P[s]) + nll
        pe = r - Q[s]
        Q[s] = Q[s] + pe}}}
  nll}
```

## decay+ blank

learning rate set as 1.

```{r}
function(par, a) {
  a = a[with(a, order(start)), ]
  nll = 0
  if (par[1] < 0 | par[1] > 50 |
      par[2] < 0 | par[2] > 1 |
      par[3] < 0 | par[3] > 1) {
    nll = Inf
  } else {
    Q = c(0, 0)
    date = rep(a$start[1], 2)
    t = c(0, 0)
    P <- vector()
    rewards = a$dooropened
    sides = ceiling(a$corner/2)
    nows = a$start
    rew = c(0,0)
    for (i in seq_along(sides)) {
      r = rewards[i]
      s = sides[i]
      now = nows[i]
      t = as.numeric(difftime(now, date, units = 'mins'))
      date[s] = now
      if (is.finite(s) & is.finite(r)) {
        decay = ifelse(rew == 1, par[2], par[3])
        Q[s] = exp( -(t[s]) * decay[s] ) * Q[s]  
        tempQ = exp( -(t[-s]) * decay[-s] ) * Q[-s]
        P[s] = exp(par[1] * Q[s]) / 
          (sum(exp(par[1] * Q[s]), exp(par[1] * tempQ)))
        if(P[s] < .001){P[s] = .001}
        if(P[s] > .999){P[s] = .999}
        nll = -log(P[s]) + nll
        pe = r - Q[s]
        Q[s] = Q[s] + pe
        rew[s] = r}}}
  nll}
```

## reproval

Probability rises along with interval between the subsequent choices 
Restriction put on the value - max 11h
termed also `reproval660`

```{r}
function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50 |
        par[3] < 0 | par[3] > 1) {
      nll = Inf
    } else {
      Q = c(0, 0)
      P <- vector()
      b0 = 0
      rewards = a$dooropened
      sides = ceiling(a$corner / 2)
      previous = lag(sides)
      previous[1] = 1
      intervals = a$intervalb
      intervals[1] = 0
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        w = previous[i]
        t = intervals[i]
        if (is.finite(s) & is.finite(r)) { 
          P = exp(par[2] * Q) / sum(exp(par[2] * Q))
          b0 = log(P[w] / (1 - P[w]))
          if(t > 660) t = 660
          P[w] = exp(b0 + par[3] * t) / 
            (1 + exp(b0 + par[3] * t))
          P[-w] = 1 - P[w]
          if(any(P < .001)){
            index = which(P < .001)
            P[index] = .001; P[-(index)] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s] 
          Q[s] = Q[s] + (par[1] * pe)}}}
    nll}
```

## random

Probability of each choice set as indifference point 0.5

```{r, eval = F}
dmodel %>%
  group_by(tag) %>%
  summarise(n = length(which(is.finite(corner)&is.finite(dooropened)))) %>%
  mutate(name = name, aic = calculateAIC(0, n * -log(0.5)))}
```

## bandit-4-arm

Applied on sequence of all visits. Water corners reward value equals 0.5

`{r} dataset: dmodel4arm`

```{r}
 function(par, a) {
    a = a[with(a, order(start)), ]
    nll = 0
    if (par[1] < 0 | par[1] > 1 |
        par[2] < 0 | par[2] > 50) {
      nll = Inf
    } else {
      Q = c(0, 0, 0, 0)
      P <- vector()
      rewards = a$dooropened
      sides = a$corner
      for (i in seq_along(sides)) {
        r = rewards[i]
        s = sides[i]
        if (is.finite(s) & is.finite(r)) {
          P = exp(par[2] * Q) / sum(exp(par[2] * Q))
          if(P[s] < .001){P[s] = .001}
          if(P[s] > .999){P[s] = .999}
          nll = -log(P[s]) + nll
          pe = r - Q[s]
          Q[s] = Q[s] + (par[1] * pe)}}}
    nll}
```

***

# Remarks {.tabset .tabset-fade}

## data

```{r echo = F, eval = TRUE}
dmodel %>%
  mutate(tag = as.character(tag)) %>%
  dplyr::left_join(select(manimal, tag, substance), by = "tag") %>%
  dplyr::group_by(exp, substance) %>%
  summarise(n.animal = length(unique(tag)),
            start = start[1],
            end = end[n()])
```

## initials

initials set:

```{r} initials.beta = seq(0.25, 15, by = 0.50)```

```{r} initials.default = seq(0.05, 1, by = 0.05)```

which differs from the original values. The new grid is a bit sparser.

```{r eval = TRUE, echo = FALSE, fig.height=7, fig.width=6}
(expand.grid(
  alpha = seq(0.05, 1, by = 0.05),
  beta = seq(0.25, 15, by = 0.25)) %>%
  ggplot(aes(x = alpha, y = beta))+
  geom_point()+
  scale_y_continuous(limits = c(0,50))+
  labs(caption = "original")) + 
  (expand.grid(
  alpha = seq(0.05, 1, by = 0.05),
  beta = seq(0.25, 15, by = 0.50)) %>%
  ggplot(aes(x = alpha, y = beta))+
  geom_point()+
  scale_y_continuous(limits = c(0,50))+
  labs(caption = "new, used here")) 
```
